\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{float}
\usepackage{svg}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{tikz}
\usepackage{nth}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage[margin=1in]{geometry}

% Custom commands
\newcommand{\ts}{\textsubscript}

% Page semantics
\pagestyle{fancy}
\fancyhead[L]{\slshape\MakeUppercase{APSC 210}}
\fancyhead[R]{\slshape Muchen He}
\fancyfoot{}
\fancyfoot[C]{\thepage}

\parindent 0ex

% Meta
\author{Muchen He}
\title{APSC 210 Work Term Report}
\begin{document}
\begin{titlepage}
\begin{center}
\vspace*{3in}
\line(1, 0){400}\\
\Huge{\textbf{Work Term 2}}\\[0.2cm]
\large{\textbf{Career Development Report}}\\[1cm]
\Large{\textbf{APSC 210}}\\
\textbf{University of British Columbia}\\
\line(1, 0){400}\\
\vfill
\Large{Muchen He}\\
\large{Associate Developer, BioWare Edmonton}\\
44638154\\

\today \\
\end{center}
\end{titlepage}

% Table of contents
\setcounter{secnumdepth}{3}
\tableofcontents
\thispagestyle{empty}
\clearpage

% list of tables and figures
\thispagestyle{empty}
\listoffigures 
\listoftables
\newpage

\setcounter{page}{1}
\setcounter{section}{-1}

% Starting of report content
\section{Introduction}\label{introduction}

BioWare, founded in 1995, is a video game studio based in Edmonton, AB. Now it is a division of Electronic Arts (EA). The studio is infamous for its story-driven games with rich, branched quests including franchises such as Mass Effect and Dragon Age \cite{bioware} \cite{bioware-wiki} \cite{bioware-list}.

There is a pipeline of games the studio outputs, the latest one being Anthem. 

My position is an associate developer on the UI/UX team for the game Anthem. 

This section introduces the industry sector where I am currently working and any future industry sector(s) I wish to work within. \\
\\
This section also outlines the subject and purpose of the report (states briefly why the report is written and what it is intended to achieve). As well as the scope (breadth and limitations of the treatment of the subject). And the plan of development (outlines the company and its mandate, the division, if applicable, and your position within the company). \\
\\


\subsection{Outline}\label{introduction-outline}

This report serves to probe the progression of career development. This report is written with intent to achieve helping us gauge our current desired career path by reviewing the skills obtained throughout the work term, as well as future desired skills that would be necessary for future careers. \\
\\
The report is broken down into four parts to help us understand what is it we need to proceed in our career development: industry in current work term, current skills being obtained, desired future industry, and transferable skills that might aid us reaching there.\\
\\
\textit{Work Term Industry} (section \ref{work-term-industry}) provides insight the industry with which we are currently working and competing in. This section outlines the company's position and its competitions in the gaming and or online entertainment and content delivery industry.

\subsection{Scope}\label{introduction-scope}

\subsection{Industry}\label{introduction-industry}

\subsection{Company}\label{introduction-company}

\section{Work Term Industry}\label{work-term-industry}

One competitor in the industry, Rockstar, and their most recent products Grand Theft Auto V (GTA 5) has become the most profitable product in the industry \cite{IGN-gta5}. With a total revenue of \$6 billion, it has made "more money than any film, book, or game".

\section{Obtained Skills}\label{obtained-skills}

\section{Desired Future Industry}\label{desired-future-industry}

\section{Transferable Skills}\label{transferable-skills}

\section*{Conclusion}\label{conclusion}
\addcontentsline{toc}{section}{Conclusion}

\begin{thebibliography}{}
% Bibliography

\bibitem{bioware}
BioWare | Rich Stories, Unforgettable Characters, And Vast Worlds. (2018). Retrieved May 23, 2018, from http://www.bioware.com/en/ 

\bibitem{bioware-wiki}
BioWare. (2018, May 23). Retrieved May 23, 2018, from https://en.wikipedia.org/wiki/BioWare

\bibitem{bioware-wiki-list}
List of BioWare video games. (2018, May 22). Retrieved May 23, 2018, from https://en.wikipedia.org/wiki/List\_of\_BioWare\_video\_games

\bibitem{VG247-bf5}
Nunneley, S. (2018, May 8). Battlefield 5 will feature "unique battles" and new challenges, Anthem to be designed around player input. VG247. Retrieved May 8, 2018, from https://www.vg247.com/2018/05/08/battlefield-5-unique-battles-challenges-anthem/

\bibitem{IGN-gta5}
Arif, S. (2018, April 9). GTA 5 Has Made More Money Than Any Film, Book, or Game, Says Analyst. Retrieved May 10, 2018, from http://ca.ign.com/articles/2018/04/09/gta-5-has-made-more-money-than-any-film-book-or-game-says-analyst

\end{thebibliography}

\end{document}